### 2020-03-09 figheatmap_R0.tex
new figures!!!!!!

% Created by tikzDevice version 0.12.3 on 2020-03-09 11:51:36
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (397.48,325.21);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,325.21);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (397.48,325.21);
\end{scope}
\begin{scope}
\path[clip] ( 34.16, 30.69) rectangle (338.79,302.56);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 34.16, 30.69) rectangle (338.79,302.56);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 44.28) --
	(338.79, 44.28);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 71.47) --
	(338.79, 71.47);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 98.65) --
	(338.79, 98.65);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,125.84) --
	(338.79,125.84);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,153.03) --
	(338.79,153.03);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,180.22) --
	(338.79,180.22);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,207.40) --
	(338.79,207.40);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,234.59) --
	(338.79,234.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,261.78) --
	(338.79,261.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,288.96) --
	(338.79,288.96);

\path[draw=drawColor,line width= 0.3pt,line join=round] (110.31, 30.69) --
	(110.31,302.56);

\path[draw=drawColor,line width= 0.3pt,line join=round] (262.63, 30.69) --
	(262.63,302.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 30.69) --
	(338.79, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 57.87) --
	(338.79, 57.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 85.06) --
	(338.79, 85.06);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,112.25) --
	(338.79,112.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,139.43) --
	(338.79,139.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,166.62) --
	(338.79,166.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,193.81) --
	(338.79,193.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,221.00) --
	(338.79,221.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,248.18) --
	(338.79,248.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,275.37) --
	(338.79,275.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,302.56) --
	(338.79,302.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 30.69) --
	( 34.16,302.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (186.47, 30.69) --
	(186.47,302.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (338.79, 30.69) --
	(338.79,302.56);
\node[inner sep=0pt,outer sep=0pt,anchor=south west,rotate=  0.00] at ( 35.25,  32.05) {
	\pgfimage[width=303.25pt,height=269.15pt,interpolate=false]{figheatmap_R0_ras1}};
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,192.10) --
	( 35.87,193.81) --
	( 36.35,194.30) --
	( 38.51,196.53) --
	( 38.55,196.57) --
	( 40.75,198.92) --
	( 41.05,199.25) --
	( 42.95,201.34) --
	( 43.50,201.97) --
	( 45.14,203.83) --
	( 45.87,204.68) --
	( 47.34,206.41) --
	( 48.16,207.40) --
	( 49.54,209.08) --
	( 50.38,210.12) --
	( 51.74,211.84) --
	( 52.52,212.84) --
	( 53.93,214.69) --
	( 54.59,215.56) --
	( 56.13,217.64) --
	( 56.60,218.28) --
	( 58.33,220.69) --
	( 58.54,221.00) --
	( 60.43,223.71) --
	( 60.53,223.85) --
	( 62.26,226.43) --
	( 62.72,227.14) --
	( 64.03,229.15) --
	( 64.92,230.54) --
	( 65.76,231.87) --
	( 67.12,234.07) --
	( 67.43,234.59) --
	( 69.06,237.31) --
	( 69.32,237.74) --
	( 70.64,240.03) --
	( 71.51,241.56) --
	( 72.18,242.75) --
	( 73.68,245.46) --
	( 73.71,245.53) --
	( 75.13,248.18) --
	( 75.91,249.66) --
	( 76.55,250.90) --
	( 77.94,253.62) --
	( 78.11,253.96) --
	( 79.28,256.34) --
	( 80.30,258.44) --
	( 80.60,259.06) --
	( 81.88,261.78) --
	( 82.50,263.12) --
	( 83.13,264.50) --
	( 84.35,267.21) --
	( 84.70,268.01) --
	( 85.54,269.93) --
	( 86.70,272.65) --
	( 86.90,273.11) --
	( 87.83,275.37) --
	( 88.95,278.09) --
	( 89.09,278.45) --
	( 90.03,280.81) --
	( 91.09,283.53) --
	( 91.29,284.04) --
	( 92.12,286.25) --
	( 93.14,288.96) --
	( 93.49,289.91) --
	( 94.13,291.68) --
	( 95.10,294.40) --
	( 95.69,296.06) --
	( 96.05,297.12) --
	( 96.98,299.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 90.39) --
	( 34.45, 90.50) --
	( 36.35, 91.21) --
	( 38.55, 92.05) --
	( 40.75, 92.91) --
	( 41.50, 93.22) --
	( 42.95, 93.81) --
	( 45.14, 94.73) --
	( 47.34, 95.69) --
	( 47.90, 95.94) --
	( 49.54, 96.67) --
	( 51.74, 97.69) --
	( 53.75, 98.65) --
	( 53.93, 98.75) --
	( 56.13, 99.84) --
	( 58.33,100.97) --
	( 59.10,101.37) --
	( 60.53,102.14) --
	( 62.72,103.35) --
	( 64.02,104.09) --
	( 64.92,104.61) --
	( 67.12,105.92) --
	( 68.57,106.81) --
	( 69.32,107.28) --
	( 71.51,108.69) --
	( 72.78,109.53) --
	( 73.71,110.15) --
	( 75.91,111.68) --
	( 76.70,112.25) --
	( 78.11,113.27) --
	( 80.30,114.93) --
	( 80.35,114.97) --
	( 82.50,116.66) --
	( 83.76,117.68) --
	( 84.70,118.47) --
	( 86.90,120.36) --
	( 86.95,120.40) --
	( 89.09,122.33) --
	( 89.94,123.12) --
	( 91.29,124.40) --
	( 92.76,125.84) --
	( 93.49,126.57) --
	( 95.42,128.56) --
	( 95.69,128.84) --
	( 97.88,131.23) --
	( 97.92,131.28) --
	(100.08,133.75) --
	(100.29,134.00) --
	(102.28,136.40) --
	(102.53,136.72) --
	(104.47,139.19) --
	(104.66,139.43) --
	(106.67,142.14) --
	(106.69,142.15) --
	(108.61,144.87) --
	(108.87,145.25) --
	(110.44,147.59) --
	(111.07,148.56) --
	(112.18,150.31) --
	(113.26,152.06) --
	(113.85,153.03) --
	(115.44,155.75) --
	(115.46,155.78) --
	(116.97,158.47) --
	(117.66,159.74) --
	(118.43,161.18) --
	(119.83,163.90) --
	(119.86,163.97) --
	(121.17,166.62) --
	(122.05,168.48) --
	(122.45,169.34) --
	(123.69,172.06) --
	(124.25,173.32) --
	(124.88,174.78) --
	(126.03,177.50) --
	(126.45,178.52) --
	(127.13,180.22) --
	(128.20,182.93) --
	(128.65,184.12) --
	(129.22,185.65) --
	(130.21,188.37) --
	(130.84,190.16) --
	(131.17,191.09) --
	(132.09,193.81) --
	(132.99,196.53) --
	(133.04,196.70) --
	(133.85,199.25) --
	(134.69,201.97) --
	(135.24,203.80) --
	(135.50,204.68) --
	(136.28,207.40) --
	(137.04,210.12) --
	(137.44,211.55) --
	(137.78,212.84) --
	(138.50,215.56) --
	(139.20,218.28) --
	(139.63,220.03) --
	(139.87,221.00) --
	(140.53,223.71) --
	(141.17,226.43) --
	(141.79,229.15) --
	(141.83,229.35) --
	(142.39,231.87) --
	(142.98,234.59) --
	(143.55,237.31) --
	(144.03,239.63) --
	(144.11,240.03) --
	(144.65,242.75) --
	(145.18,245.46) --
	(145.69,248.18) --
	(146.20,250.90) --
	(146.23,251.05) --
	(146.69,253.62) --
	(147.17,256.34) --
	(147.63,259.06) --
	(148.09,261.78) --
	(148.42,263.79) --
	(148.54,264.50) --
	(148.97,267.21) --
	(149.40,269.93) --
	(149.81,272.65) --
	(150.22,275.37) --
	(150.62,278.09) --
	(150.62,278.09) --
	(151.01,280.81) --
	(151.39,283.53) --
	(151.76,286.25) --
	(152.13,288.96) --
	(152.48,291.68) --
	(152.82,294.27) --
	(152.84,294.40) --
	(153.18,297.12) --
	(153.51,299.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (337.41, 48.53) --
	(335.21, 48.76) --
	(333.01, 48.99) --
	(330.81, 49.24) --
	(328.62, 49.49) --
	(326.69, 49.72) --
	(326.42, 49.75) --
	(324.22, 50.02) --
	(322.02, 50.29) --
	(319.83, 50.58) --
	(317.63, 50.87) --
	(315.43, 51.18) --
	(313.23, 51.50) --
	(311.04, 51.83) --
	(308.84, 52.17) --
	(307.21, 52.44) --
	(306.64, 52.53) --
	(304.44, 52.90) --
	(302.25, 53.28) --
	(300.05, 53.68) --
	(297.85, 54.09) --
	(295.65, 54.53) --
	(293.46, 54.98) --
	(292.63, 55.15) --
	(291.26, 55.45) --
	(289.06, 55.94) --
	(286.86, 56.45) --
	(284.67, 56.99) --
	(282.47, 57.55) --
	(281.27, 57.87) --
	(280.27, 58.14) --
	(278.07, 58.76) --
	(275.88, 59.41) --
	(273.68, 60.09) --
	(272.15, 60.59) --
	(271.48, 60.81) --
	(269.28, 61.57) --
	(267.09, 62.37) --
	(264.89, 63.22) --
	(264.66, 63.31) --
	(262.69, 64.11) --
	(260.49, 65.06) --
	(258.39, 66.03) --
	(258.30, 66.07) --
	(256.10, 67.14) --
	(253.90, 68.29) --
	(253.06, 68.75) --
	(251.70, 69.51) --
	(249.51, 70.82) --
	(248.47, 71.47) --
	(247.31, 72.22) --
	(245.11, 73.73) --
	(244.48, 74.19) --
	(242.92, 75.36) --
	(240.98, 76.90) --
	(240.72, 77.12) --
	(238.52, 79.03) --
	(237.88, 79.62) --
	(236.32, 81.11) --
	(235.11, 82.34) --
	(234.13, 83.39) --
	(232.63, 85.06) --
	(231.93, 85.88) --
	(230.39, 87.78) --
	(229.73, 88.63) --
	(228.36, 90.50) --
	(227.53, 91.68) --
	(226.51, 93.22) --
	(225.34, 95.07) --
	(224.81, 95.94) --
	(223.26, 98.65) --
	(223.14, 98.87) --
	(221.82,101.37) --
	(220.94,103.16) --
	(220.50,104.09) --
	(219.27,106.81) --
	(218.74,108.03) --
	(218.12,109.53) --
	(217.06,112.25) --
	(216.55,113.62) --
	(216.06,114.97) --
	(215.13,117.68) --
	(214.35,120.09) --
	(214.25,120.40) --
	(213.42,123.12) --
	(212.65,125.84) --
	(212.15,127.67) --
	(211.91,128.56) --
	(211.22,131.28) --
	(210.56,134.00) --
	(209.95,136.67) --
	(209.94,136.72) --
	(209.35,139.43) --
	(208.79,142.15) --
	(208.25,144.87) --
	(207.76,147.53) --
	(207.75,147.59) --
	(207.26,150.31) --
	(206.79,153.03) --
	(206.35,155.75) --
	(205.92,158.47) --
	(205.56,160.90) --
	(205.52,161.18) --
	(205.12,163.90) --
	(204.75,166.62) --
	(204.39,169.34) --
	(204.04,172.06) --
	(203.71,174.78) --
	(203.39,177.50) --
	(203.36,177.75) --
	(203.08,180.22) --
	(202.78,182.93) --
	(202.49,185.65) --
	(202.22,188.37) --
	(201.95,191.09) --
	(201.69,193.81) --
	(201.44,196.53) --
	(201.20,199.25) --
	(201.16,199.64) --
	(200.96,201.97) --
	(200.73,204.68) --
	(200.51,207.40) --
	(200.30,210.12) --
	(200.09,212.84) --
	(199.89,215.56) --
	(199.70,218.28) --
	(199.51,221.00) --
	(199.32,223.71) --
	(199.14,226.43) --
	(198.97,229.15) --
	(198.97,229.24) --
	(198.80,231.87) --
	(198.64,234.59) --
	(198.47,237.31) --
	(198.32,240.03) --
	(198.17,242.75) --
	(198.02,245.46) --
	(197.87,248.18) --
	(197.73,250.90) --
	(197.59,253.62) --
	(197.46,256.34) --
	(197.33,259.06) --
	(197.20,261.78) --
	(197.08,264.50) --
	(196.95,267.21) --
	(196.83,269.93) --
	(196.77,271.48) --
	(196.72,272.65) --
	(196.60,275.37) --
	(196.49,278.09) --
	(196.38,280.81) --
	(196.27,283.53) --
	(196.17,286.25) --
	(196.07,288.96) --
	(195.97,291.68) --
	(195.87,294.40) --
	(195.77,297.12) --
	(195.68,299.84);

>>>>

% Created by tikzDevice version 0.12.3 on 2020-03-09 13:46:06
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (361.35,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,289.08);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (361.35,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 34.16, 30.69) rectangle (302.65,266.42);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 34.16, 30.69) rectangle (302.65,266.42);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 42.47) --
	(302.65, 42.47);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 66.05) --
	(302.65, 66.05);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16, 89.62) --
	(302.65, 89.62);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,113.19) --
	(302.65,113.19);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,136.77) --
	(302.65,136.77);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,160.34) --
	(302.65,160.34);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,183.91) --
	(302.65,183.91);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,207.49) --
	(302.65,207.49);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,231.06) --
	(302.65,231.06);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.16,254.64) --
	(302.65,254.64);

\path[draw=drawColor,line width= 0.3pt,line join=round] (101.28, 30.69) --
	(101.28,266.42);

\path[draw=drawColor,line width= 0.3pt,line join=round] (235.53, 30.69) --
	(235.53,266.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 30.69) --
	(302.65, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 54.26) --
	(302.65, 54.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 77.83) --
	(302.65, 77.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,101.41) --
	(302.65,101.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,124.98) --
	(302.65,124.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,148.55) --
	(302.65,148.55);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,172.13) --
	(302.65,172.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,195.70) --
	(302.65,195.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,219.28) --
	(302.65,219.28);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,242.85) --
	(302.65,242.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,266.42) --
	(302.65,266.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 30.69) --
	( 34.16,266.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (168.41, 30.69) --
	(168.41,266.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (302.65, 30.69) --
	(302.65,266.42);
\node[inner sep=0pt,outer sep=0pt,anchor=south west,rotate=  0.00] at ( 35.12,  31.86) {
	\pgfimage[width=267.28pt,height=233.38pt,interpolate=false]{figheatmap_R0_ras1}};
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16,170.65) --
	( 35.66,172.13) --
	( 36.09,172.56) --
	( 37.99,174.49) --
	( 38.03,174.53) --
	( 39.97,176.56) --
	( 40.23,176.84) --
	( 41.90,178.66) --
	( 42.40,179.20) --
	( 43.84,180.82) --
	( 44.48,181.56) --
	( 45.78,183.06) --
	( 46.50,183.91) --
	( 47.71,185.37) --
	( 48.45,186.27) --
	( 49.65,187.76) --
	( 50.34,188.63) --
	( 51.59,190.23) --
	( 52.17,190.99) --
	( 53.52,192.79) --
	( 53.94,193.34) --
	( 55.46,195.44) --
	( 55.65,195.70) --
	( 57.31,198.06) --
	( 57.40,198.18) --
	( 58.92,200.42) --
	( 59.33,201.03) --
	( 60.49,202.77) --
	( 61.27,203.98) --
	( 62.01,205.13) --
	( 63.21,207.04) --
	( 63.48,207.49) --
	( 64.92,209.85) --
	( 65.14,210.22) --
	( 66.31,212.20) --
	( 67.08,213.53) --
	( 67.67,214.56) --
	( 68.99,216.92) --
	( 69.02,216.97) --
	( 70.27,219.28) --
	( 70.96,220.55) --
	( 71.52,221.63) --
	( 72.74,223.99) --
	( 72.89,224.28) --
	( 73.93,226.35) --
	( 74.83,228.17) --
	( 75.09,228.70) --
	( 76.22,231.06) --
	( 76.77,232.23) --
	( 77.32,233.42) --
	( 78.39,235.78) --
	( 78.70,236.46) --
	( 79.44,238.13) --
	( 80.47,240.49) --
	( 80.64,240.89) --
	( 81.47,242.85) --
	( 82.45,245.21) --
	( 82.58,245.52) --
	( 83.40,247.56) --
	( 84.34,249.92) --
	( 84.51,250.37) --
	( 85.25,252.28) --
	( 86.14,254.64) --
	( 86.45,255.45) --
	( 87.02,256.99) --
	( 87.87,259.35) --
	( 88.39,260.79) --
	( 88.71,261.71) --
	( 89.53,264.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.16, 82.46) --
	( 34.41, 82.55) --
	( 36.09, 83.16) --
	( 38.03, 83.89) --
	( 39.97, 84.64) --
	( 40.63, 84.91) --
	( 41.90, 85.42) --
	( 43.84, 86.22) --
	( 45.78, 87.05) --
	( 46.27, 87.26) --
	( 47.71, 87.90) --
	( 49.65, 88.79) --
	( 51.42, 89.62) --
	( 51.59, 89.70) --
	( 53.52, 90.65) --
	( 55.46, 91.63) --
	( 56.14, 91.98) --
	( 57.40, 92.64) --
	( 59.33, 93.69) --
	( 60.48, 94.33) --
	( 61.27, 94.79) --
	( 63.21, 95.92) --
	( 64.49, 96.69) --
	( 65.14, 97.10) --
	( 67.08, 98.32) --
	( 68.20, 99.05) --
	( 69.02, 99.59) --
	( 70.96,100.92) --
	( 71.65,101.41) --
	( 72.89,102.30) --
	( 74.83,103.73) --
	( 74.87,103.76) --
	( 76.77,105.24) --
	( 77.87,106.12) --
	( 78.70,106.80) --
	( 80.64,108.44) --
	( 80.69,108.48) --
	( 82.58,110.15) --
	( 83.33,110.84) --
	( 84.51,111.95) --
	( 85.81,113.19) --
	( 86.45,113.83) --
	( 88.15,115.55) --
	( 88.39,115.80) --
	( 90.32,117.87) --
	( 90.36,117.91) --
	( 92.26,120.05) --
	( 92.45,120.27) --
	( 94.20,122.35) --
	( 94.42,122.62) --
	( 96.13,124.77) --
	( 96.30,124.98) --
	( 98.07,127.32) --
	( 98.08,127.34) --
	( 99.78,129.70) --
	(100.01,130.03) --
	(101.39,132.05) --
	(101.94,132.89) --
	(102.93,134.41) --
	(103.88,135.93) --
	(104.40,136.77) --
	(105.80,139.12) --
	(105.82,139.15) --
	(107.14,141.48) --
	(107.75,142.59) --
	(108.43,143.84) --
	(109.66,146.20) --
	(109.69,146.25) --
	(110.84,148.55) --
	(111.63,150.17) --
	(111.98,150.91) --
	(113.07,153.27) --
	(113.57,154.37) --
	(114.12,155.63) --
	(115.13,157.98) --
	(115.50,158.87) --
	(116.10,160.34) --
	(117.04,162.70) --
	(117.44,163.72) --
	(117.94,165.06) --
	(118.82,167.41) --
	(119.38,168.96) --
	(119.66,169.77) --
	(120.47,172.13) --
	(121.26,174.49) --
	(121.31,174.63) --
	(122.02,176.84) --
	(122.76,179.20) --
	(123.25,180.79) --
	(123.48,181.56) --
	(124.17,183.91) --
	(124.84,186.27) --
	(125.19,187.51) --
	(125.49,188.63) --
	(126.12,190.99) --
	(126.74,193.34) --
	(127.12,194.86) --
	(127.33,195.70) --
	(127.91,198.06) --
	(128.47,200.42) --
	(129.02,202.77) --
	(129.06,202.94) --
	(129.55,205.13) --
	(130.07,207.49) --
	(130.57,209.85) --
	(131.00,211.86) --
	(131.07,212.20) --
	(131.54,214.56) --
	(132.01,216.92) --
	(132.46,219.28) --
	(132.91,221.63) --
	(132.93,221.76) --
	(133.34,223.99) --
	(133.76,226.35) --
	(134.17,228.70) --
	(134.58,231.06) --
	(134.87,232.80) --
	(134.97,233.42) --
	(135.35,235.78) --
	(135.73,238.13) --
	(136.09,240.49) --
	(136.45,242.85) --
	(136.81,245.21) --
	(136.81,245.21) --
	(137.15,247.56) --
	(137.48,249.92) --
	(137.81,252.28) --
	(138.13,254.64) --
	(138.45,256.99) --
	(138.74,259.24) --
	(138.76,259.35) --
	(139.06,261.71) --
	(139.35,264.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (301.44, 46.16) --
	(299.50, 46.36) --
	(297.56, 46.56) --
	(295.62, 46.77) --
	(293.69, 46.99) --
	(291.99, 47.19) --
	(291.75, 47.22) --
	(289.81, 47.45) --
	(287.88, 47.69) --
	(285.94, 47.93) --
	(284.00, 48.19) --
	(282.07, 48.46) --
	(280.13, 48.73) --
	(278.19, 49.02) --
	(276.26, 49.32) --
	(274.82, 49.54) --
	(274.32, 49.63) --
	(272.38, 49.94) --
	(270.45, 50.28) --
	(268.51, 50.62) --
	(266.57, 50.98) --
	(264.64, 51.36) --
	(262.70, 51.75) --
	(261.97, 51.90) --
	(260.76, 52.16) --
	(258.83, 52.58) --
	(256.89, 53.03) --
	(254.95, 53.49) --
	(253.02, 53.98) --
	(251.96, 54.26) --
	(251.08, 54.49) --
	(249.14, 55.03) --
	(247.20, 55.59) --
	(245.27, 56.19) --
	(243.92, 56.62) --
	(243.33, 56.81) --
	(241.39, 57.47) --
	(239.46, 58.16) --
	(237.52, 58.89) --
	(237.32, 58.97) --
	(235.58, 59.67) --
	(233.65, 60.49) --
	(231.79, 61.33) --
	(231.71, 61.37) --
	(229.77, 62.30) --
	(227.84, 63.29) --
	(227.09, 63.69) --
	(225.90, 64.35) --
	(223.96, 65.48) --
	(223.05, 66.05) --
	(222.03, 66.70) --
	(220.09, 68.01) --
	(219.54, 68.40) --
	(218.15, 69.42) --
	(216.45, 70.76) --
	(216.22, 70.95) --
	(214.28, 72.61) --
	(213.71, 73.12) --
	(212.34, 74.41) --
	(211.28, 75.48) --
	(210.41, 76.38) --
	(209.09, 77.83) --
	(208.47, 78.55) --
	(207.11, 80.19) --
	(206.53, 80.93) --
	(205.32, 82.55) --
	(204.59, 83.57) --
	(203.69, 84.91) --
	(202.66, 86.52) --
	(202.20, 87.26) --
	(200.83, 89.62) --
	(200.72, 89.81) --
	(199.56, 91.98) --
	(198.78, 93.53) --
	(198.39, 94.33) --
	(197.31, 96.69) --
	(196.85, 97.75) --
	(196.30, 99.05) --
	(195.36,101.41) --
	(194.91,102.60) --
	(194.48,103.76) --
	(193.66,106.12) --
	(192.97,108.21) --
	(192.89,108.48) --
	(192.16,110.84) --
	(191.48,113.19) --
	(191.04,114.78) --
	(190.83,115.55) --
	(190.22,117.91) --
	(189.64,120.27) --
	(189.10,122.58) --
	(189.09,122.62) --
	(188.57,124.98) --
	(188.07,127.34) --
	(187.60,129.70) --
	(187.16,132.00) --
	(187.15,132.05) --
	(186.72,134.41) --
	(186.31,136.77) --
	(185.92,139.12) --
	(185.55,141.48) --
	(185.23,143.59) --
	(185.19,143.84) --
	(184.84,146.20) --
	(184.51,148.55) --
	(184.20,150.91) --
	(183.89,153.27) --
	(183.60,155.63) --
	(183.32,157.98) --
	(183.29,158.20) --
	(183.04,160.34) --
	(182.78,162.70) --
	(182.53,165.06) --
	(182.28,167.41) --
	(182.04,169.77) --
	(181.82,172.13) --
	(181.60,174.49) --
	(181.38,176.84) --
	(181.35,177.19) --
	(181.18,179.20) --
	(180.98,181.56) --
	(180.78,183.91) --
	(180.59,186.27) --
	(180.41,188.63) --
	(180.23,190.99) --
	(180.06,193.34) --
	(179.89,195.70) --
	(179.73,198.06) --
	(179.57,200.42) --
	(179.42,202.77) --
	(179.42,202.85) --
	(179.27,205.13) --
	(179.13,207.49) --
	(178.98,209.85) --
	(178.85,212.20) --
	(178.71,214.56) --
	(178.58,216.92) --
	(178.45,219.28) --
	(178.33,221.63) --
	(178.21,223.99) --
	(178.09,226.35) --
	(177.97,228.70) --
	(177.86,231.06) --
	(177.75,233.42) --
	(177.64,235.78) --
	(177.54,238.13) --
	(177.48,239.48) --
	(177.44,240.49) --
	(177.33,242.85) --
	(177.24,245.21) --
	(177.14,247.56) --
	(177.04,249.92) --
	(176.95,252.28) --
	(176.86,254.64) --
	(176.77,256.99) --
	(176.69,259.35) --
	(176.60,261.71) --
	(176.52,264.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (301.44,101.56) --
	(299.50,102.46) --
	(297.56,103.39) --
	(296.81,103.76) --
	(295.62,104.35) --
	(293.69,105.35) --
	(292.23,106.12) --
	(291.75,106.38) --
	(289.81,107.44) --
	(287.98,108.48) --
	(287.88,108.54) --
	(285.94,109.67) --
	(284.03,110.84) --
	(284.00,110.85) --
	(282.07,112.07) --
	(280.34,113.19) --
	(280.13,113.34) --
	(278.19,114.64) --
	(276.90,115.55) --
	(276.26,116.00) --
	(274.32,117.41) --
	(273.66,117.91) --
	(272.38,118.88) --
	(270.62,120.27) --
	(270.45,120.40) --
	(268.51,121.99) --
	(267.76,122.62) --
	(266.57,123.64) --
	(265.05,124.98) --
	(264.64,125.36) --
	(262.70,127.15) --
	(262.50,127.34) --
	(260.76,129.02) --
	(260.08,129.70) --
	(258.83,130.97) --
	(257.79,132.05) --
	(256.89,133.01) --
	(255.61,134.41) --
	(254.95,135.14) --
	(253.53,136.77) --
	(253.02,137.37) --
	(251.56,139.12) --
	(251.08,139.71) --
	(249.68,141.48) --
	(249.14,142.17) --
	(247.88,143.84) --
	(247.20,144.75) --
	(246.16,146.20) --
	(245.27,147.46) --
	(244.52,148.55) --
	(243.33,150.32) --
	(242.94,150.91) --
	(241.43,153.27) --
	(241.39,153.33) --
	(239.98,155.63) --
	(239.46,156.51) --
	(238.59,157.98) --
	(237.52,159.86) --
	(237.25,160.34) --
	(235.97,162.70) --
	(235.58,163.42) --
	(234.73,165.06) --
	(233.65,167.19) --
	(233.54,167.41) --
	(232.38,169.77) --
	(231.71,171.19) --
	(231.27,172.13) --
	(230.20,174.49) --
	(229.77,175.45) --
	(229.17,176.84) --
	(228.17,179.20) --
	(227.84,180.00) --
	(227.20,181.56) --
	(226.26,183.91) --
	(225.90,184.85) --
	(225.35,186.27) --
	(224.47,188.63) --
	(223.96,190.04) --
	(223.62,190.99) --
	(222.80,193.34) --
	(222.03,195.61) --
	(222.00,195.70) --
	(221.22,198.06) --
	(220.46,200.42) --
	(220.09,201.61) --
	(219.73,202.77) --
	(219.01,205.13) --
	(218.32,207.49) --
	(218.15,208.07) --
	(217.65,209.85) --
	(216.99,212.20) --
	(216.35,214.56) --
	(216.22,215.07) --
	(215.73,216.92) --
	(215.12,219.28) --
	(214.53,221.63) --
	(214.28,222.66) --
	(213.95,223.99) --
	(213.39,226.35) --
	(212.84,228.70) --
	(212.34,230.92) --
	(212.31,231.06) --
	(211.79,233.42) --
	(211.28,235.78) --
	(210.78,238.13) --
	(210.41,239.95) --
	(210.29,240.49) --
	(209.82,242.85) --
	(209.35,245.21) --
	(208.90,247.56) --
	(208.47,249.86) --
	(208.46,249.92) --
	(208.02,252.28) --
	(207.59,254.64) --
	(207.18,256.99) --
	(206.77,259.35) --
	(206.53,260.78) --
	(206.38,261.71) --
	(205.98,264.07);
